formula1

### 2020-02-19 inst/formula1.Rmd
typos

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library("hyper2")
library("magrittr")
```

@@

Each row is a driver and each column (after the first) a venue.  We
see that Hamilton, the first row, came second in Australia, first in
China, second in Bahrain, fourthin Russia, and so on.  In the first
columnm, we see the result from Australia in which Hamilton came
second, Vettel first, Bottas third, and so on.  Notation used also
includes six different classes of no-score such as "Ret" for retired,
"WD" for withdrawn, and so on.  I now define a bespoke R function that
translates data of this type into a log-likelihood function using the
`hyper2` package.  The function is similar to, but slightly different
from, the analysis in `eurovision.R`.

>>>>

```{r setup, include=FALSE}
set.seed(0)
knitr::opts_chunk$set(echo = TRUE)
library("hyper2")
library("magrittr")
```

@@

Each row is a driver and each column (after the first) a venue.  We
see that Hamilton, the first row, came second in Australia, first in
China, second in Bahrain, fourth in Russia, and so on.  In the first
column, we see the result from Australia (AUS) in which Hamilton came
second, Vettel first, Bottas third, and so on.  Notation used also
includes six different classes of no-score such as "Ret" for retired,
"WD" for withdrawn, and so on.  I now define a bespoke R function that
translates data of this type into a log-likelihood function using the
`hyper2` package.  The function is similar to, but slightly different
from, the analysis in `eurovision.R`.
